CODECHECK: An open-science initiative for the independent execution of computations underlying research articles during peer review improves reproducibility

### 2021-01-25 codecheck-paper.tex
add abstract, change link colours, update title

\documentclass[12pt]{article}
\usepackage{f1000_styles}
\usepackage[numbers]{natbib}
\usepackage{hyperref}
\usepackage{url}
\usepackage{setspace}

@@

\begin{document}
\title{CODECHECK: An open-science initiative for the independent execution of computations underlying research articles}
\author[1,$\ast$]{Daniel~N\"{u}st \orcid{0000-0002-0024-5046} \github{nuest} \twitter{nordholmen}}
\author[2,$\ast$]{Stephen~J~Eglen \orcid{0000-0001-8607-8025} \github{sje30} \twitter{StephenEglen}}
\affil[1]{Institute for Geoinformatics, University of M\"unster, Germany; \email{daniel.nuest@uni-muenster.de}}
\affil[2]{Department of Applied Mathematics and Theoretical Physics, University of Cambridge, GB; \email{sje30@cam.ac.uk}}
\affil[$\ast$]{Contributed equally}
\affil[$$]{Public project for this article is at \url{https://github.com/codecheckers/paper}}
\maketitle
\begin{abstract}
  This is a draft paper that we hope to submit to F1000R (and perhaps
  as a preprint before) in the coming weeks.
  \ldots{}
\end{abstract}

>>>>

\documentclass[12pt]{article}
\usepackage{f1000_styles}
\usepackage[numbers]{natbib}
\usepackage{hyperref}
\hypersetup{colorlinks=false, pdfborderstyle={/S/U/W 1}, pdfborder=0 0 1}
\usepackage{url}
\usepackage{setspace}

@@

\begin{document}
%\title{CODECHECK: An open-science initiative for the independent execution of computations underlying research articles}
\title{CODECHECK: An open-science initiative for the independent execution of computations underlying research articles during peer review improves reproducibility}
\author[1,$\ast$]{Daniel~N\"{u}st \orcid{0000-0002-0024-5046} \github{nuest} \twitter{nordholmen}}
\author[2,$\ast$]{Stephen~J~Eglen \orcid{0000-0001-8607-8025} \github{sje30} \twitter{StephenEglen}}
\affil[1]{Institute for Geoinformatics, University of M\"unster, Germany; \email{daniel.nuest@uni-muenster.de}}
\affil[2]{Department of Applied Mathematics and Theoretical Physics, University of Cambridge, GB; \email{sje30@cam.ac.uk}}
\affil[$\ast$]{Contributed equally}
\affil[$$]{Public project for this article is at \url{https://github.com/codecheckers/paper}.}
\maketitle
\begin{abstract}
  The scientific paper falls short of effectively communicating computational research.
  To break out of the stalemate between multiple lacks of incentives, guidance, benefits, recognitions, and reproducibility, we propose to introduce execution of workflows underlying research articles as part of peer review.
  The CODECHECK system relies on five principles and can be integrated into review and publications processes in multiple ways, which we describe along multiple dimensions (importance, who, openness, when).
  We demonstrate CODECHECK with 25 reproductions of diverse scientific publications in collaboration with academic publishers and conferences.
  These CODECHECKs show that asking for reproducible workflows in a collaborative review can effectively improve executability.
  CODECHECK relies on free infrastructure and open tools.
  While it has clear limitations, it can be a building block in the open-science and publishing ecosystems to improve the reproducibility, appreciation, and potentially quality of non-textual research artefacts.
\end{abstract}
